Estimating dark matter halo concentration using the integrated mass profile

### 2016-04-17 paper/paper.tex
paper full version

\begin{figure}
\begin{center}
  \includegraphics[width=0.47\textwidth]{avg_foff_bolshoi.pdf}
\end{center}
\vspace{-0.5cm}
\caption{Average value of the relative error in the concentration
  estimate, $\avg{|D|}$, as a function of the particle number $N$ in
  the set of mock halos. Different symbols represent different
  methods. The new method provides the most accurate estimate at fixed
  particle number.  
    \label{fig:downsampling}}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=0.45\textwidth]{error_conc_bolshoi.pdf}
\end{center}
\vspace{-0.5cm}
\caption{Average value of the relative error in the concentration
  estimate, $\avg{|D|}$, as a function of the particle number $N$ in
  the set of mock halos. Different symbols represent different
  methods. The new method provides the most accurate estimate at fixed
  particle number.  
    \label{fig:downsampling_err}}
\end{figure}

>>>>

\begin{figure}
\begin{center}
  \includegraphics[width=0.49\textwidth]{avg_foff_bolshoi.pdf}
\end{center}
\vspace{-0.5cm}
\caption{Average value of the fractional offset ($f_{\rm off}$Eq. \ref{eq:f_off})
  between the concentration in a halo at high resolution versus its
  downsampled  versions. 
  Each point is the result of 100 downsampling iterations.
  The velocity method noticeably overestimates the
  concentration up to a factor of $0.25$, while the new method only
  underestimates the concentrations by up to a factor of $0.05$.
    \label{fig:downsampling}}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=0.47\textwidth]{error_conc_bolshoi.pdf}
\end{center}
\vspace{-0.5cm}
\caption{Uncertainties on different concentration estimates.
  The large symbols show the standard deviation of the fractional
  offset ($f_{\rm off}$ Eq. \ref{eq:f_off}) from the downsampling
  experiments.  
  The small dots correspond to the $1-\sigma$ uncertainty on the
  concentration for each halo as estimated by the MCMC algorithm in
  used for the new method.
  Uncertainties from fluctuations on the halo particle number are
  larger than the statistical uncertainties from the fitting process. 
  \label{fig:downsampling_err}}
\end{figure}
